Grow with the flow: a latitudinal cline in physiology is associated with more variable precipitation in \textit{Erythranthe cardinalis}

### 2017-09-02 ms/ms.Rnw
revising ms

  # Function for bootstrapping effect sizes
  fn <- function(merMod) {
    x <- anova(merMod)
    ret <- x[c("PopID", "PopID:TempTrt", "PopID:WaterTrt"), "Mean Sq"]
    ret <- c(ret, x["PopID", "Mean Sq"] - x["PopID:TempTrt", "Mean Sq"],
             x["PopID", "Mean Sq"] - x["PopID:WaterTrt", "Mean Sq"])
    ret
  }

  ciMerModLER <- confint(mm, method = "boot", FUN = fn, nsim = 1e3, seed = 50717035,
                         parallel = "multicore", ncpus = 2L, level = 0.95)
  ciMerModLER <- as.data.frame(ciMerModLER)
  fit <- anova(mm)
  ciMerModLER$estimate <- c(fit[c("PopID", "PopID:TempTrt", "PopID:WaterTrt"), "Mean Sq"],
                            fit["PopID", "Mean Sq"] - fit["PopID:TempTrt", "Mean Sq"],
                            fit["PopID", "Mean Sq"] - fit["PopID:WaterTrt", "Mean Sq"])
  rownames(ciMerModLER) <- c("PopID", "PopID:TempTrt", "PopID:WaterTrt", 
                             "PopID - PopID:TempTrt", "PopID - PopID:WaterTrt")
  rm(fit)

@@

  # Confidence intervals on effect size (mean squared error)
  ciMerModSER <- confint(mm, method = "boot", FUN = fn, nsim = 1e3, seed = 46887099,
                         parallel = "multicore", ncpus = 2L)
  ciMerModSER <- as.data.frame(ciMerModSER)
  fit <- anova(mm)
  ciMerModSER$estimate <- c(fit[c("PopID", "PopID:TempTrt", "PopID:WaterTrt"), "Mean Sq"],
                            fit["PopID", "Mean Sq"] - fit["PopID:TempTrt", "Mean Sq"],
                            fit["PopID", "Mean Sq"] - fit["PopID:WaterTrt", "Mean Sq"])
  rownames(ciMerModSER) <- c("PopID", "PopID:TempTrt", "PopID:WaterTrt", 
                             "PopID - PopID:TempTrt", "PopID - PopID:WaterTrt")
  rm(fit)

@@

  # Confidence intervals on effect size (mean squared error)
  ciMerModPhoto <- confint(mm, method = "boot", FUN = fn, nsim = 1e3, 
                           seed = 12657909, parallel = "multicore", ncpus = 2L)
  ciMerModPhoto <- as.data.frame(ciMerModPhoto)
  fit <- anova(mm)
  ciMerModPhoto$estimate <- c(fit[c("PopID", "PopID:TempTrt", "PopID:WaterTrt"), "Mean Sq"],
                              fit["PopID", "Mean Sq"] - fit["PopID:TempTrt", "Mean Sq"],
                              fit["PopID", "Mean Sq"] - fit["PopID:WaterTrt", "Mean Sq"])
  rownames(ciMerModPhoto) <- c("PopID", "PopID:TempTrt", "PopID:WaterTrt", 
                               "PopID - PopID:TempTrt", "PopID - PopID:WaterTrt")
  rm(fit)

@@

  ##### TEMPORARY: CODE TO EXPORT FIGURE FOR TALK #####
  # d <- subset(master, !is.na(master$DiedFromStress))
  # x <- tapply(d$DiedFromStress, list(d$PopID, d$WaterTrt, d$TempTrt), function(X) 1 - length(which(X)) / length(X))
  # 
  # pdf("~/Google Drive/Talks/JobTalk/3_Mimulus/DroughtResponse.pdf", w = 5.5, h = 5, useDingbats = F)
  # par(mai = c(1, 1.5, 0.25, 0.25))
  # 
  # plot(focClim$bio16_avg, x[, "Dry", "Hot"] / x[, "Wet", "Hot"], axes = F, frame.plot = T,
  #      pch = 21, col = "black", bg = primShade0, cex = 2, type = "n",
  #      xlab = "Precipitation of Wettest Quarter (mm)", 
  #      ylab = "Relative Survivorship\n(Hot/Dry : Hot/Wet)", cex.lab = 1.5)
  # points(focClim$bio16_avg, x[, "Dry", "Hot"] / x[, "Wet", "Hot"], pch = 21, col = "black", 
  #        bg = primShade0, cex = 1.5, lwd = 2)
  # axis(1, lwd = 0, lwd.ticks = 1)
  # axis(2, lwd = 0, lwd.ticks = 1, las = 1)
  # dev.off()
  #

@@

  pathFig <- "/Users/cdmuir/Google Drive/CardAdapt/ms/Figures"

pdf(paste0(pathFig, "/FigureS_EffectSizes.pdf"), 12, 4, useDingbats = F)
par(mai = c(1, 1, 0.5, 0.1), mfrow = c(1, 3))

for (mod in list(ciMerModLER, ciMerModSER, ciMerModPhoto)) {

#  assign("mod", mod)

  plot(0, 0, type = "n", axes = FALSE, frame.plot = TRUE,
       ylim = range(mod), xlim = c(1, 5),
       xlab = "", ylab = "Effect size (Mean squared error)", cex.lab = 1.5,
       main = )

  abline(h = 0, lty = 2, col = "grey50")
  for (i in 1:5) {
    lines(rep(i, 2), c(mod[i, "2.5 %"], mod[i, "97.5 %"]))
    points(i, mod[i, "estimate"], pch = 19)
  }

  axis(2, las = 1, lwd = 0, lwd.ticks = 1)
  clip(-100, 100, -100, 100)
  text(x = 1:5, y = grconvertY(-0.025, "npc", "user"), srt = 45, pos = 2, 
       labels = c("Pop", "Pop x Temp", "Pop x Water", "Pop - Pop x Temp",
                  "Pop - Pop x Water"))

@@

  ##### TEMPORARY VERSION FOR TALK #####
  # Plot latitude versus PC1
#   pdf("~/Google Drive/Talks/JobTalk/3_Mimulus/Figure_PC1vLat.pdf", 5.5, 5, useDingbats = F)
#   par(mai = c(1, 1.5, 0.25, 0.25))
#   plot(focClim$Lat, focClim$PC1, xlim = c(32, 44), ylim = c(-4, 4), axes = F,
#     frame.plot = T, type = "n", xlab = "", ylab = "")
#   title(xlab = "Latitude", cex.lab = 1.5)
#   title(ylab = "TraitPC1", cex.lab = 2, line = 5)
#   title(ylab = substitute(plain(Principal~Component~1)~group("(", x, ")"), 
#     list(x = pve)))
#   axis(1, at = seq(32, 44, 4), labels = c(expression(32*degree), 
# 		expression(36*degree), expression(40*degree), expression(44*degree)), 
# 		lwd = 0, lwd.ticks = 1) 
#   axis(2, at = seq(-4, 4, 2), las = 1, lwd = 0, lwd.ticks = 1)    
#   fitLat <- lm(PC1 ~ Latitude, data = focClim)
#   
# 	# Label y-axis from slow to fast growth
# 	mtext(c("Slow\nGrowth", "Fast\nGrowth"), 2, at = c(-4, 4), cex = 1.25, 
# 				font = 3, las = 1, line = 4, adj = 0.5)
# 
#   # polygon of confidence intervals
#   x <- seq(min(focClim$Latitude), max(focClim$Latitude), l = 1e3)
#   u <- predict(fitLat, new = data.frame(Latitude = x))
#   s <- sqrt(sapply(x, function(X) t(c(1, X)) %*% vcov(fitLat) %*% c(1, X)))
#   confInt <- data.frame(lowerCI = qnorm(0.025, u, s), 
#   											upperCI = qnorm(0.975, u, s))
#   polygon(c(x, rev(x)), c(confInt$lowerCI, rev(confInt$upperCI)), 
#     col = "grey", border = NA)
#   lines(x, confInt$lowerCI, lwd = 2, lty = 2)
#   lines(x, confInt$upperCI, lwd = 2, lty = 2)
#   lines(range(focClim$Lat), rev(range(predict(fitLat))), lwd = 2)
#   points(focClim$Lat, focClim$PC1, pch = 21, col = "black", bg = primShade0, 
#   			 cex = 1.5, lwd = 2)
#   
#   # P-value
#   text(grconvertX(0.95, "npc"), grconvertY(0.95, "npc"), adj = c(1, 1),
# 	     labels = bquote(italic(P) == .(round(summary(fitLat)[[4]][2, 4], 3))))
# 
#   dev.off()

>>>>

  # Function for bootstrapping effect sizes
  fn <- function(merMod) {
    x <- anova(merMod)
    ret <- x[c("PopID", "PopID:TempTrt", "PopID:WaterTrt", "PopID:TempTrt:WaterTrt"), "Mean Sq"]
    ret <- c(ret, x["PopID", "Mean Sq"] - x["PopID:TempTrt", "Mean Sq"],
             x["PopID", "Mean Sq"] - x["PopID:WaterTrt", "Mean Sq"],
             x["PopID", "Mean Sq"] - x["PopID:TempTrt:WaterTrt", "Mean Sq"])
    ret
  }

  ciMerModLER <- confint(mm, method = "boot", FUN = fn, nsim = 1e3, seed = 50717035,
                         parallel = "multicore", ncpus = 2L, level = 0.95)
  ciMerModLER <- as.data.frame(ciMerModLER)
  fit <- anova(mm)
  ciMerModLER$estimate <- c(fit[c("PopID", "PopID:TempTrt", "PopID:WaterTrt", 
                                  "PopID:TempTrt:WaterTrt"), "Mean Sq"],
                            fit["PopID", "Mean Sq"] - fit["PopID:TempTrt", "Mean Sq"],
                            fit["PopID", "Mean Sq"] - fit["PopID:WaterTrt", "Mean Sq"],
                            fit["PopID", "Mean Sq"] - fit["PopID:TempTrt:WaterTrt", "Mean Sq"])
  rownames(ciMerModLER) <- c("PopID", "PopID:TempTrt", "PopID:WaterTrt", "PopID:TempTrt:WaterTrt", 
                             "PopID - PopID:TempTrt", "PopID - PopID:WaterTrt",
                             "PopID - PopID:TempTrt:WaterTrt")
  rm(fit)

@@

  # Confidence intervals on effect size (mean squared error)
  ciMerModSER <- confint(mm, method = "boot", FUN = fn, nsim = 1e3, seed = 46887099,
                         parallel = "multicore", ncpus = 2L)
  ciMerModSER <- as.data.frame(ciMerModSER)
  fit <- anova(mm)
  ciMerModSER$estimate <- c(fit[c("PopID", "PopID:TempTrt", "PopID:WaterTrt", 
                                  "PopID:TempTrt:WaterTrt"), "Mean Sq"],
                            fit["PopID", "Mean Sq"] - fit["PopID:TempTrt", "Mean Sq"],
                            fit["PopID", "Mean Sq"] - fit["PopID:WaterTrt", "Mean Sq"],
                            fit["PopID", "Mean Sq"] - fit["PopID:TempTrt:WaterTrt", "Mean Sq"])
  rownames(ciMerModSER) <- c("PopID", "PopID:TempTrt", "PopID:WaterTrt", "PopID:TempTrt:WaterTrt", 
                             "PopID - PopID:TempTrt", "PopID - PopID:WaterTrt",
                             "PopID - PopID:TempTrt:WaterTrt")
  rm(fit)

@@

  # Confidence intervals on effect size (mean squared error)
  ciMerModPhoto <- confint(mm, method = "boot", FUN = fn, nsim = 1e3, 
                           seed = 12657909, parallel = "multicore", ncpus = 2L)
  ciMerModPhoto <- as.data.frame(ciMerModPhoto)
  fit <- anova(mm)
  ciMerModPhoto$estimate <- c(fit[c("PopID", "PopID:TempTrt", "PopID:WaterTrt", 
                                  "PopID:TempTrt:WaterTrt"), "Mean Sq"],
                            fit["PopID", "Mean Sq"] - fit["PopID:TempTrt", "Mean Sq"],
                            fit["PopID", "Mean Sq"] - fit["PopID:WaterTrt", "Mean Sq"],
                            fit["PopID", "Mean Sq"] - fit["PopID:TempTrt:WaterTrt", "Mean Sq"])
  rownames(ciMerModPhoto) <- c("PopID", "PopID:TempTrt", "PopID:WaterTrt", 
                               "PopID:TempTrt:WaterTrt", "PopID - PopID:TempTrt", 
                               "PopID - PopID:WaterTrt",
                               "PopID - PopID:TempTrt:WaterTrt")
  rm(fit)

@@

@@

  # pathFig <- "/Users/cdmuir/Google Drive/CardAdapt/ms/Figures" # for debug

  pdf(paste0(pathFig, "/FigureS_EffectSizes.pdf"), 8, 8, useDingbats = F)
  par(mai = c(1, 1, 0.5, 0.1), mfrow = c(2, 2))

  mods <- list(ciMerModLER, ciMerModSER, ciMerModPhoto, ciMerModMort)
  for (i in 1:length(mods)) {

    mod <- mods[[i]]
    main <- c("Leaf expansion", "Stem elongation", "Photosynthesis", "Mortality")[i]
    plot(0, 0, type = "n", axes = FALSE, frame.plot = TRUE,
         ylim = range(mod), xlim = c(1, 7),
         xlab = "", ylab = "Effect size", cex.lab = 1.5,
         main = main)

    abline(h = 0, lty = 2, col = "grey50")
    for (i in 1:7) {
    lines(rep(i, 2), c(mod[i, "2.5 %"], mod[i, "97.5 %"]))
      points(i, mod[i, "estimate"], pch = 19)
    }

    axis(2, las = 1, lwd = 0, lwd.ticks = 1)
    clip(-100, 100, -100, 100)
    text(x = 1:7, y = grconvertY(-0.025, "npc", "user"), srt = 45, pos = 2, 
         labels = c("Pop", "Pop x Temp", "Pop x Water", "Pop x Temp x Water", 
                    "Pop - Pop x Temp", "Pop - Pop x Water", "Pop - Pop x Temp x Water"))

@@
